---
title: "Tolerance and Intolerance in the GSS"
author: "Fauzia Waqar"
format: pdf
execute:
  echo: false
  warning: false
  message: false
---
```{r}
source("01_gss_tolerance.R")
```

# Replication
```{r}
fig1_rep
```{r}
fig2_rep
fig5_rep
fig1_ext
fig2_ext
fig5_ext
happy_plot
tv_plot
```

**1. Problems and tricky parts**

The answer codes were different for each question, and the library question was reversed. "Don't know" was hidden, so I had to find it. My Figure 5 is about 0.98, but the paper's is about 0.8. I do not know why.

**2. What Mondak and Sanders found**

Figure 1 shows people became less intolerant, from about 7 to about 5.5. But the authors say this may be because people's feelings about some groups changed. Figure 2 shows this: people became more accepting of homosexuals, but not of racists. Figure 5 shows most people still said "no" at least once. So tolerance grew only a little.

**3. What has changed since 1998**

The score kept falling slowly, then went up a little at the end. Acceptance of homosexuals kept growing. Intolerance toward racists went up at the end. Figure 5 stayed flat.




